caDDS: Community Assisted Distributed Database for Sequences

### 2020-06-24 Paper2020ACM/Paper2020.tex
Revision June 24 5pm

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
working draft (insert kulang when info is ready):
 Genomic data the past few years have grown exponentially with the technology barely keeping up. The problem faced by genome researchers is the large data set and difficulty transferring the files. Previous distributed databases are either not meant for genomic data, or difficult to replicate. This paper lays the groundwork for a distributed database that is designed to easily scale to accommodate bigger storage, and also reduces the data speed bottleneck faced by centralized databases. The proposed system has a master node and data nodes. Data nodes should theoretically increase data transfer speeds even as the number of users increase. (to be updated based on conclusion) While current databases(e.g. NCBI) have more data, more users, and a live platform. The proposed system is aimed towards a smaller community, with more frequent and localized data, which the data storage can easily be expanded as the need arises. A recommendation is to implement the system and make the code public for the use of other communities.
\end{abstract}

@@

We want to acknowledge our advisers for giving the idea for out thesis. And for answering our many questions about genomics. Writing this paper overlapped with the covid19 pandemic which changed a big portion of the scope of this thesis. We thank our advisers for making this work manageable during this pandemic crisis.
\end{acks}

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
Genomic data the past few years have grown exponentially with the technology barely keeping up. The problem faced by genome researchers is the large data set and difficulty transferring the files. Previous distributed databases are either not meant for genomic data, or difficult to replicate. This paper lays the groundwork for a distributed database that is designed to easily scale to accommodate bigger storage, and also reduces the data speed bottleneck faced by centralized databases. The proposed system has a master node and data nodes. Data nodes should theoretically increase data transfer speeds even as the number of users increase. (to be updated based on conclusion) While current databases(e.g. NCBI) have more data, more users, and a live platform. The proposed system is aimed towards a smaller community, with more frequent and localized data, which the data storage can easily be expanded as the need arises. The proposed system is also theoretically faster as long as there are multiple working data nodes. A recommendation is to implement the system and make the code public for the use of other communities.
\end{abstract}

@@

We want to acknowledge our advisers for giving the idea for our thesis. And for answering our many questions about genomics. Writing this paper overlapped with the covid19 pandemic which changed a big portion of the scope of this thesis. We thank our advisers for making this work manageable during this pandemic crisis.
\end{acks}

### 2020-06-24 Paper2020ACM/Presentation.tex
June 24 2pm
Revision June 24 5pm

\subsection{Database Concepts}
\begin{frame}{Database}
  \begin{itemize}   
    \item Technology for data storage
    \item Technology needed to be developed to resolve the growing storage concern
  \end{itemize}
\end{frame}

@@

\begin{frame}{Database Principles}
  \begin{itemize}   
    \item consistency
    \item availability
    \item partition tolerance
  \end{itemize}
\end{frame}

@@

@@

\subsection{Comparisons}
\begin{frame}{Speed Comparisons}
  \begin{itemize}   
    \item simple time complexity chart
    \item faster si caDDS ofc 
    \item 
  \end{itemize}
\end{frame}

\begin{frame}{Final Comparisons}
  \begin{itemize}   
    \item caDDS is scalable, easy for community, has docu hehe
    \item NCBI is one, stable, widely used
    \item 
  \end{itemize}
\end{frame}

>>>>

\subsection{Database Concepts}
\begin{frame}{Database}
  \begin{itemize}   
    \item Database is the technology for data storage
    \item Technology needed to be developed to resolve the growing storage concern
  \end{itemize}
\end{frame}

@@

\begin{frame}{Database Principles}

  \begin{itemize}   
    \item consistency
    \item availability
    \item partition tolerance
  \end{itemize}
\end{frame}

@@

\begin{frame}{Table}
% Bio-related -> biological
% What's the difference between biological vs general vs FASTA
% What does general mean?
% What does biological mean? -> explain pa to
% May 3 types of data ...
   \begin{table}[]
        \begin{tabular}{|l|l|l|l|l|}
        \hline
        System      & CS/P2P/H & Available? & DL/UL speed & Type of Data \\ \hline
        BioTorrents & P2P           & No         & Depends                    & Biological  \\ \hline
        SeqTorr     & H             & No         & Fast (PH server)           & FASTA        \\ \hline
        PeerDB      & P2P           & No         & Depends                    & General      \\ \hline
        NCBI        & CS            & Yes        & Slow (US server)           & Biological  \\ \hline
        \end{tabular}
    \end{table} 
\end{frame}

@@

\subsection{Comparisons}
\begin{frame}{Speed Comparisons}
  \begin{itemize}   
    \item base method
    \item proposed method
    \item 
  \end{itemize}
\end{frame}

\begin{frame}{Final Comparisons}
  \begin{itemize}   
    \item base method
    \item proposed method
    \item 
  \end{itemize}
\end{frame}
